Towards a Classification of Sporadic $j$-invariants

### 2023-03-15 TeX/draft.tex
Updates from Overleaf

% Nongross real and imaginary parts
\renewcommand{\Im}{\operatorname{Im}}
\renewcommand{\Re}{\operatorname{Re}}
\newcommand{\Q}{\bQ}
\newcommand{\Z}{\bZ}

\newcommand{\davidnote}[1]{\marginpar{\footnotesize{\textcolor{Plum}{David: #1}}}}

@@

\begin{theorem}
Let $x=[E,P]\in X_1(N)$ be a non-CM sporadic point with $j(E) \in \Q$. Fix an equation of $E/\Q$, and let $N_E$ denote its conductor. Suppose
\begin{itemize}
\item$N_E \leq 500,000$,
\item $N_E$ is only divisible prime primes $p \leq 7$, or
\item $N_E=p \leq 200,000,000$ for some prime number $p$.
\end{itemize}
Then $j(E) =-140625/8$ or $-9317$.
\end{theorem}

@@

\begin{enumerate}
    \item Compute the adelic image of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm. Represent the output as some \emph{level} $M$ together with a subgroup $G$ of $\GL_2(\Z/M\Z)$.
\end{enumerate}
\end{algorithm}

>>>>

% Nongross real and imaginary parts
\renewcommand{\Im}{\operatorname{Im}}
\renewcommand{\Re}{\operatorname{Re}}
\newcommand{\Q}{\bQ}
\newcommand{\Z}{\bZ}
\newcommand{\filip}[1]{{\color{cyan} \textsf{$\sun\sun\sun$ Filip: [#1]}}}
\newcommand{\davidnote}[1]{\marginpar{\footnotesize{\textcolor{Plum}{David: #1}}}}

@@

\begin{theorem}
Let $x=[E,P]\in X_1(N)$ be a non-CM sporadic point with $j(E) \in \Q$. Fix an equation of $E/\Q$, and let $N_E$ denote its conductor. Suppose
\begin{itemize}
\item$N_E \leq 500{,}000$,
\item $N_E$ is only divisible prime primes $p \leq 7$, or
\item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
\end{itemize}
Then $j(E) =-140625/8$ or $-9317$.
\end{theorem}

@@

\begin{enumerate}
    \item Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm. Represent the output as some \emph{level} $M$ together with a subgroup $G$ of $\GL_2(\Z/M\Z)$.

    \item Reduce level.

    \item For all $12 < b \mid M$ compute the minimum degree of the field of definition of a point with respect to $G \mod b$, the image of $G$ in $\GL_2(\Z/b\Z)$. (For that, compute the orbits of $\langle G, -G \rangle \mod b$ on $\bP^1(\Z/b\Z)$. Sort the orbits by size. Return ) \filip{We need to look at the orbits of $\langle G, -G \rangle \mod b$ on $(\Z/b\Z)^2$, not $\bP^1(\Z/b\Z)$. If we consider the action on $\bP^1(\Z/b\Z)$, the orbits might be too small and hence the degree we get. Furthermore, it is necessary to consider only the elements of $(\Z/b\Z)^2$ of order $b$.}
\end{enumerate}
\end{algorithm}

(In the \texttt{Magma} implementation, we have to be careful that \texttt{Magma} uses right actions, but in our mathematics, we use left action. We therefore use the transposes of the matrices in $\GL_2(\Z/M\Z)$.)
